WTCIII-Figures

### 2015-06-25 markdown/WTC3_figures.Rmd
more minor tweaks to figure markdown

![aci](aci_curves.png)
Figure2. Predicted photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated and ambient temperature treatments. ACi curves were developed at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). ACi curves were taken once on well watered trees before the initiation of the drought treatment.

@@

```{r wateruse, fig.width=8, fig.height=10}
source("master_scripts/wateruse.R")
```  
Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) (a) and response of leaf photosynthesis rates to stomatal conductance (b) for sun and shade leaves at elevated and ambient temperature treatments. For (a)  lines represent predictions from the optimal ITE model with k=0.05 and a specific g1 value for each leaf type and treatment. For (b) dashed lines represent 95% confidence intervals from a general additive model with k=5.

@@

>>>>

```{r acicurves, fig.width=8, fig.height=6}
source("master_scripts/aci_curves.R")
```  
Figure2. Predicted photosynthetic CO~2~ response (ACi) curves for sun and shade leaves at elevated and ambient temperature treatments. ACi curves were developed at 25°C and at saturating light (1800 $\mu$mols m^-1^ s^-1^). ACi curves were taken once on well watered trees before the initiation of the drought treatment.

@@

```{r wateruse, fig.width=8, fig.height=10}
source("master_scripts/wateruse.R")
```  
Figure 3. Response of instantaneous water use efficiency (ITE) to leaf vapor pressure deficit (VPD) (a) and response of leaf photosynthesis rates to stomatal conductance (b) for sun and shade leaves at elevated and ambient temperature treatments. For (a)  lines represent predictions from the optimal ITE model with a g1 value for each leaf type and treatment. For (b) dashed lines represent 95% confidence intervals from a general additive model with k=5.

@@

```{r table, results="asis"}
ge_data <- read.csv("master_scripts/ge_table.csv")
ge_tab <- ge_data[,1:8]

colnames(ge_tab) <- c("Leaf", "Temperature", "Light Level", "Photosynthesis", "g~s~","g~m~",
                      "Ci", "Transpiration")
pandoc.table(ge_tab, caption = "Gas exchange data for sun and shade leaves", split.cells = c(1,1,1,1,1,1,1,1))
```
